workshop

### 2023-02-24 scripts/workshop/workshop.Rmd
add text
try to filter out data after epidemic
filter out months after peak prev

Standard deviations from the mean
This chunk attempts to characterize each wetland in terms of how exceptional they are compared to other wetlands in terms of abundance, cc, and temp
The idea is that if certain wetlands tend to be highly abundant with high community competence and lower temperatures, then we might expect them to be a perfect environment for ranavirus to thrive. 
```{r}
comm_data <- readRDS(here("processed_data","comm_data.rds"))
comm_data %>% mutate(mean = mean(size), sd = sd(size), var = mean(size)-size, size = size)
comm_effect <- comm_data %>% filter(MeanWaterTempPredC>0) %>% mutate(size_sds = (mean(size)-size)/sd(size),
                                    cc_sds = (mean(cc)-cc)/sd(cc),
                                    temp_sds = ((mean(MeanWaterTempPredC)-MeanWaterTempPredC)/sd(MeanWaterTempPredC))*-1) #multiply by -1 to make it opposite because

@@

Redo analysis (effect size) with only the data from months before and including the peak. Rationale is that we are most interested in the features of a wetland that make it good or bad for an epidemic to occur. After an epidemic begins and peaks, the conditions of the wetland during the decline of the epidemic may not be as important since there are less susceptibles and parasite may be dying out. We'll see

>>>>

Standard deviations from the mean
This chunk attempts to characterize each wetland in terms of how exceptional they are compared to other wetlands in terms of abundance, cc, and temp
The idea is that if certain wetlands tend to be highly abundant with high community competence and lower temperatures, then we might expect them to be a perfect environment for ranavirus to thrive. 
```{r}
comm_data <- readRDS(here("processed_data","comm_data.rds"))
comm_data %>% mutate(mean = mean(size), sd = sd(size), var = mean(size)-size, size = size)
comm_effect <- comm_data %>% filter(MeanWaterTempPredC>0) %>% mutate(size_sds = (mean(size)-size)/sd(size),
                                    cc_sds = (mean(cc)-cc)/sd(cc),
                                    temp_sds = ((mean(MeanWaterTempPredC)-MeanWaterTempPredC)/sd(MeanWaterTempPredC))*-1) #multiply by -1 to make it opposite

@@

Redo analysis (effect size) with only the data from months before and including the peak. Rationale is that we are most interested in the features of a wetland that make it good or bad for an epidemic to occur. After an epidemic begins and peaks, the conditions of the wetland during the decline of the epidemic may not be as important since there are less susceptibles and parasite may be dying out. We'll see.

```{r}
comm_data_1 <- readRDS(here("processed_data","comm_data.rds"))
comm_data_1$month.n <- as.numeric(gsub("Month","",comm_data_1$Month.1))
comm_data_1 %<>% group_by(WetAltID) %>% mutate(max_mo = ifelse(Prevalence == max(Prevalence),month.n,0)) 
comm_data_1 %<>% group_by(WetAltID) %>% mutate(max_mo=max(max_mo))

comm_data_2 <- comm_data_1 %>% group_by(WetAltID) %>% filter(!month.n>max_mo)
```

```{r}
comm_data_2 %>% mutate(mean = mean(size), sd = sd(size), var = mean(size)-size, size = size)
comm_effect_2 <- comm_data_2 %>% filter(MeanWaterTempPredC>0) %>% mutate(size_sds = (mean(size)-size)/sd(size),
                                    cc_sds = (mean(cc)-cc)/sd(cc),
                                    temp_sds = ((mean(MeanWaterTempPredC)-MeanWaterTempPredC)/sd(MeanWaterTempPredC))*-1) #multiply by -1 to make it opposite

effect_summ_2 <- comm_effect_2 %>% group_by(WetAltID) %>% summarize(size_over = sum(size_sds>0),
                                                                size_sum = sum(size_sds),
                                                                cc_over = sum(cc_sds>0),
                                                                cc_sum = sum(cc_sds),
                                                                temp_over = sum(temp_sds>0),
                                                                temp_sum = sum(temp_sds))
```

```{r}
plot_ly(data = effect_summ_2, x=effect_summ_2$temp_over, y=effect_summ_2$size_over, z=effect_summ_2$cc_over, 
        type="scatter3d", mode="markers", color=as.factor(effect_summ_2$WetAltID))

plot_ly(data = effect_summ_2, x=effect_summ_2$temp_sum, y=effect_summ_2$size_sum, z=effect_summ_2$cc_sum, 
        type="scatter3d", mode="markers", color=as.factor(effect_summ_2$WetAltID))
```

Also, rerun dynamics without demography.
